Spfy: an integrated graph-based sequence database for real-time prediction of Escherichia coli phenotypes

### 2018-01-31 paper-webserver.tex
DEL: 3rd para in functionality section is somewhat redundant. Merged into 2nd

By supporting multiple \textit{in-silico} subtyping options, the platform functions similar to a reference laboratory, while adding support for population analyses. Subtyping options for E.coli are O-antigen, H-antigen, and VF gene determination using ECtyper \url{https://github.com/phac-nml/ecoli\_serotyping}, Shiga-toxin 1 (Stx1), Shiga-toxin 2 (Stx2), and Intimin typing using Phylotyper \cite{whiteside2017phylotyper}, and AMR annotation using the RGI program \cite{mcarthur2013comprehensive}.
Spfy also performs bioinformatics analyses: pangenome generation using Panseq \cite{laing2010pan}, statistical significance testing using SciPy \cite{jones2014scipy}, and support vector machine (SVM)-backed AMR predictions for OmniLog AMR assays using Scikit-learn \cite{pedregosa2011scikit}.

These tasks are divided into subtasks, and distributed across a built-in task queue. Results are converted to individual graphs and stored within a larger graph database. By integrating task distribution with graph storage, Spfy enables large-scale analyses, such as epidemiological associations between specific genotypes, biomarkers, host, source, and other metadata, and statistical significance testing of genome markers for user-defined groups, in real-time. Currently, the platform has been tested with XXX genome files and result storage for XX analyses modules.

@@

% group comparisons
Knowledge graphs semantically link data points using relations defined in an ontology. Spfy allows users to compare the results associated with particular genome types or metadata by storing all results in a graph structure. Comparisons can be made in real-time, as new genomes are submitted for analysis and the results stored in the existing graph. Any data type or relation in the graph is valid for analysis, such as the presence or absence of pan-genome regions against determined serotypes or other subtyping options. In addition, Spfy supports the submission of user-specified metadata, such as location or source information. Results are displayed on-screen and available for download.

>>>>

By supporting multiple \textit{in-silico} subtyping options, the platform functions similar to a reference laboratory, while adding support for population analyses. Subtyping options for \textit{E.coli} are O-antigen, H-antigen, and VF gene determination using ECtyper \url{https://github.com/phac-nml/ecoli\_serotyping}, Shiga-toxin 1 (Stx1), Shiga-toxin 2 (Stx2), and Intimin typing using Phylotyper \cite{whiteside2017phylotyper}, and AMR annotation using the RGI program \cite{mcarthur2013comprehensive}.
Spfy also performs bioinformatics analyses: pangenome generation using Panseq \cite{laing2010pan} and support vector machine (SVM)-backed AMR predictions for OmniLog AMR assays using Scikit-learn \cite{pedregosa2011scikit}.

These tasks are divided into subtasks, and distributed across a built-in task queue. Results are converted to individual graphs and stored within a larger graph database. By integrating task distribution with graph storage, Spfy enables large-scale analyses, such as epidemiological associations between specific genotypes, biomarkers, host, source, and other metadata, and statistical significance testing of genome markers for user-defined groups using SciPy \cite{jones2014scipy}. Any data type or relation in the graph is valid for analysis, such as the presence or absence of pan-genome regions against determined serotypes or other subtyping options. In addition, Spfy supports the submission of user-specified metadata, such as location or source information. Currently, the platform has been tested with XXX genome files and result storage for XX analyses modules.

@@
